Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-11-10 draft.tex
fix condition/restriction terminology throughout text

We provide a set of conditions under which perpetual unrecognized statehood is the outcome of a stationary Markov equilibrium of this game. %This requires that the patron is both willing and able to make investments sufficient to (a) offset the deterioration in the secessionists' status quo payoffs and (b) deter the international community from making investments that would induce a negotiated settlement. That is, it must be that the prospect of reunification is more important for the patron to avoid than for the international community to achieve. Additionally, in order for the status quo to persist, preferences must be such that recognition of the secessionist state is more important for the international community to avoid than for the patron to achieve; otherwise, the international community will not be able to deter the patron from making investments to instigate recognition.
Somewhat counterintuitively, in this equilibrium a patron will expend resources every period if necessary to sustain the status quo of unrecognized statehood even when the patron would prefer that the secessionists achieve recognized independence. This occurs when the international community's preferences against recognition are sufficiently strong---as is almost always likely to the case---to make it prohibitively expensive for the patron to facilitate recognition in the face of counteractivity by the international community.

@@

We next turn to presenting the model. In Section 3, we present a set of conditions under which unrecognized statehood is a stable, long-run equilibrium outcome. In Section 4, we analyze the potential effects of sanctions on the resolution of territorial disputes while Section 5 explores extensions of the model. Section 6 evaluates policy implications of the model, assessing various strategies available to outside actors that seek to induce their preferred outcomes. Section 7 concludes.

@@

\item \textit{$B_{pt} \geq \mu, \ \forall t>1$: the patron can afford to pay to maintain the status quo.}\footnote{Depending on parameters, condition (5) is more likely to be binding than condition (6). If there is great variance in budget between periods for the patron, such as a greatly reduced budget in some period $t> 1$ compared to period $1$, (6) could be binding.}

>>>>

We provide a set of parameter restrictions under which perpetual unrecognized statehood is the outcome of a stationary Markov equilibrium of this game. %This requires that the patron is both willing and able to make investments sufficient to (a) offset the deterioration in the secessionists' status quo payoffs and (b) deter the international community from making investments that would induce a negotiated settlement. That is, it must be that the prospect of reunification is more important for the patron to avoid than for the international community to achieve. Additionally, in order for the status quo to persist, preferences must be such that recognition of the secessionist state is more important for the international community to avoid than for the patron to achieve; otherwise, the international community will not be able to deter the patron from making investments to instigate recognition.
Somewhat counterintuitively, in this equilibrium a patron will expend resources every period if necessary to sustain the status quo of unrecognized statehood even when the patron would prefer that the secessionists achieve recognized independence. This occurs when the international community's preferences against recognition are sufficiently strong---as is almost always likely to the case---to make it prohibitively expensive for the patron to facilitate recognition in the face of counteractivity by the international community.

@@

We next turn to presenting the model. In Section 3, we present a set of parameter restrictions under which unrecognized statehood is a stable, long-run equilibrium outcome. In Section 4, we analyze the potential effects of sanctions on the resolution of territorial disputes while Section 5 explores extensions of the model. Section 6 evaluates policy implications of the model, assessing various strategies available to outside actors that seek to induce their preferred outcomes. Section 7 concludes.

@@

\item \textit{$B_{pt} \geq \mu, \ \forall t>1$: the patron can afford to pay to maintain the status quo.}\footnote{Depending on parameters, Restriction (5) is more likely to be binding than Restriction (6). If there is great variance in budget between periods for the patron, such as a greatly reduced budget in some period $t> 1$ compared to period $1$, (6) could be binding.}
